Stage-Splitting a Modal Language

### 2014-09-29 paper/semantics.tex
fix unicode in pdf bookmarks
small fix

\section{\lang\ Statics and Dynamics}
\label{sec:semantics}

@@

This concludes stage \bbone\ evaluation of the program---we have reduced all
\bbone\ redexes, resulting in a monostaged term in \langTwo. Stage \bbtwo\
evaluation, $\tworedsym$, then reduces this to a numeral.

@@

The algorithm described above creates three different kinds of expressions which
cannot be evaluated further at a particular stage:
\begin{itemize}
\item Partial values ($\pvalsym$s) are stage \bbone\ terms that have been fully
evaluated, but which may contain stage-\bbtwo\ variables wrapped in $\next$
blocks.  In the example above, 
\verb|(|$\next \{\mathtt{\hat y}\}$\verb|,7)|.

>>>>

\section{\texorpdfstring{\lang}{λ12} Statics and Dynamics}
\label{sec:semantics}

@@

This concludes stage \bbone\ evaluation of the program---we have reduced all
stage \bbone\ redexes, resulting in a monostaged term in \langTwo. Stage \bbtwo\
evaluation, $\tworedsym$, then reduces this to a numeral.

@@

The algorithm described above creates two different kinds of expressions which
cannot be evaluated further at stage \bbone:
\begin{itemize}
\item Partial values ($\pvalsym$s) are stage \bbone\ terms that have been fully
evaluated, but which may contain stage-\bbtwo\ variables wrapped in $\next$
blocks.  In the example above, 
\verb|(|$\next \{\mathtt{\hat y}\}$\verb|,7)|.
